---
title: "p8105_hw1_cc5424"
author: "ChuqiChen"
date: "2025-09-20"
output: github_document
---
problem 1

```{r}
library(moderndive)

library(ggplot2)

data("early_january_weather")

early_january_weather
```

This dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

It includes variables including `r names(early_january_weather)`.
There are important variables such as time_hour, temperature (°C), humidity(%), wind_speed, wind_gust.
It includes hourly data from January 1, 2023, to January 15, 2023.

The mean temperature in the dataset is `r round(mean(early_january_weather$temp), 2)`°C.

```{r}
ggplot(early_january_weather, aes(y = temp, x = time_hour, color = humid))+
  geom_point()+
  labs(
    title = "Scatterplot of Temperature(y) vs Time(x)",
    y = "Temperature (°C)",
    x = "Time(hour)",
    color = "Humidity (%)"
    )

ggsave("scatterplot.pdf")
```

The x-axis represents time in hours. The y-axis represents temperature. The color of each data point corresponds to its humidity value.

Temperature generally fluctuates upward over time. It peaks during specific periods (near noon) and declines during evening hours.
A relationship exists between humidity and temperature, with lower temperatures occurring at higher humidity levels.



problem 2

```{r}
sample = rnorm(10)
```

