---
title: "p8105_hw1_cc5424"
author: "ChuqiChen"
date: "2025-09-20"
output: github_document
---
problem 1

```{r}
library(moderndive)

library(ggplot2)

data("early_january_weather")

early_january_weather
```

This dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

It includes variables including `r names(early_january_weather)`.
There are important variables such as time_hour, temperature (°C), humidity(%), wind_speed, wind_gust.
It includes hourly data from January 1, 2023, to January 15, 2023.

The mean temperature in the dataset is `r round(mean(early_january_weather$temp), 2)`°C.

```{r}
ggplot(early_january_weather, aes(y = temp, x = time_hour, color = humid))+
  geom_point()+
  labs(
    title = "Scatterplot of Temperature(y) vs Time(x)",
    y = "Temperature (°C)",
    x = "Time(hour)",
    color = "Humidity (%)"
    )

ggsave("scatterplot.pdf")
```

The x-axis represents time in hours. The y-axis represents temperature. The color of each data point corresponds to its humidity value.

Temperature generally fluctuates upward over time. It peaks during specific periods (near noon) and declines during evening hours.
A relationship exists between humidity and temperature, with lower temperatures occurring at higher humidity levels.



problem 2

```{r}
library(tidyverse)

sample1 = rnorm(10)
logical_vec = sample1 > 0
char_vec = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J")
factor_vec = factor(c("low", "medium", "high", "low", "medium", "high", "low", "medium", "high", "low"))

df = data.frame(sample1, logical_vec, char_vec, factor_vec)

mean_sample1 = mean(pull(df, sample1))
mean_sample1 
#work

mean_logical = mean(pull(df, logical_vec))
mean_logical 
#work

mean_char = mean(pull(df, char_vec))
mean_char 
#fail

mean_factor = mean(pull(df, factor_vec))
mean_factor 
#fial
```

Taking the mean works for numeric and logical vectors, but fails for character and factor vectors.

```{r eval = FALSE}
mean_numeric_logical = mean(as.numeric(logical_vec))
mean_numeric_logical

mean_numeric_char = mean(as.numeric(char_vec))
mean_numeric_char

mean_numeric_factor = mean(as.numeric(factor_vec))
mean_numeric_factor
```

What happens and why?

Logical to Numeric: R can change TRUE to 1 and FALSE to 0. I can take the mean of a logical vector because they are numbers now.

Character to Numeric: Since the characters are letters, R cannot convert them to numbers directly. So I still can not take the mean of a character vector.

Factor to Numeric: I can take the mean of factors because factors contains 3 different levels and R can give them different numbers. But the original factors represent categories, not numeric values, so the mean might not be meaningful.

Does this help explain what happens when you try to take the mean?
Yes
